The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities

### 2023-12-07 r_r/manuscript_rihe_r_r.Rmd
revising intro, adding revised tables

*During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[NAME THE UNIVERSITIES] We are still trying to figure out what happened.*
\bigskip

@@

Father Ryan High School is a Catholic school founded in 1925. Father Ryan is predominantly white (86%, 7% Black or Latinx) and received an "A" grade from Niche, meaning it is not ranked in the top 1,000 US private schools. In fall 2017, Father Ryan received visits from nine of the 14 private universities in our sample (including all the Catholic universities) and the same six public universities that visited Harpeth Hall, including two visits by the University of Alabama. Meanwhile, Christ Presbyterian Academy -- also not ranked in the top 1,000 private schools -- received visits from five private universities in our sample (including the three Christian universities Baylor, Texas Christian University, and Southern Methodist University). It also received visits from the University of Cincinatti, the University of South Carolina, the University of Alabama, University of Arkansas, and CU Boulder. Christ Presbyterian Academy was founded in 1985 and 94% of its students are white.

@@

@RN4758 analyzed recruiting visits to public high schools made by 15 public research universities in 2017. the authors found that 12 of the 15 universities made more visits to out-of-state schools than in-state schools. These out-of-state visits focused on affluent, predominantly white public schools. Set against the scholarship about declining state appropriations and growing nonresident enrollment [@RN3753; @RN3685], these results suggest that many public research universities prioritize enrollment from wealthy out-of-state students who can afford to pay nonresident tuition price.

Within scholarship on social mobility and social stratification, a multidisciplinary literature analyzes the relationship between private school and college [CITE]. This research observes strong links -- and student flows -- between private high schools and selective private universities [CITE]. To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on links between between private school and college. We argue that these two stories have become connected because public research universities increasingly target out-of-state private schools, schools that have been the domain of selective private universities.

@@

1. How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?
    - ALTERNATIVE: How does the scale of visits to private high schools vary for the public research universities and selective private universities in our sample?
1. To what extent do public research universities and selective private universities visit overlapping sets of private high schools?
1. How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?

Both private and public universities in our sample made a disproportionate number of visits to private high schools. For public research universities, visited private schools were much more likely to be out-of-state than visited public schools. Although universities visited a large number of private schools in their home region, most universities also visited a large number of private schools in the South. Private schools that received visits were predominantly white. Although partially a function of our analysis sample, public universities tended to visit lower ranked private high schools than private universities. Surprisingly, several public universities visited sectarian private high schools at a rate similar to sectarian private universities. Network analyses revealed substantial overlap in the recruiting networks of public and private research universities.

This manuscript is practically important because it provides insight about which schools universities view as "feeder schools" and -- to a limited extent -- the characteristics of students they want to enroll. Prior research finds that university recruiting efforts affect the enrollment decisions of students [CITE]. In turn, the composition of enrolled students affects the campus culture experienced by students.  Scholarship and the popular press reports that underrepresented minority students and low-income students at public flagship universities feel isolated amidst affluent, predominantly white student bodies. Racial and socioeconomic isolation negatively affects student development outcomes for isolated students and for the entire student body [CITE]. State policymakers and institutional leaders should recognize that the enrollment composition at public research universities is not the consequence of exogenous student demand, but rather the consequence of recruiting efforts that seek to grow nonresident enrollment by systematically targeting affluent, predominantly white public high schools [@RN4758] and affluent, predominantly white private high schools.
[NOTE: THESE IMPLICATIONS HAVE TO DO ABOUT TARGETING PRIVATE SCHOOLS BUT NOT TARGETING SAME SET OF SCHOOLS TARGETED BY SELECTIVE PRIVATE UNIVERSITIES]

@@

@@

\newpage
\clearpage

```{r sample-characteristics}
univ_sample <- univ_sample_df %>% 
  select(classification, univ_abbrev, rank, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_p, pctfreshwh, pctfreshbl, pctfreshap, pctfreshhi, pctfreshal)

kable(univ_sample %>% arrange(desc(classification), rank), caption = "Characteristics of universities in analysis sample") %>%
  collapse_rows(columns = 1, latex_hline = 'major', valign = 'middle') %>%
  kable_styling(latex_options = 'scale_down')
```

@@

\begin{landscape}

```{r pubu-percent-matrix}
table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))

table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))

table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
rownames(table_1mode_pubu$onemode_df) <- colnames(table_1mode_pubu$onemode_df)

rownames(table_1mode_pubu$onemode_pct_df) <- colnames(table_1mode_pubu$onemode_pct_df)

kable(table_1mode_pubu$onemode_pct_df, caption = 'One-mode public university percent matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(c(1), width = '13em') %>% 
  column_spec(c(14), width = '8.5em') %>% 
  column_spec(2:13, width = '7em') %>% 
  column_spec(c(7, 9, 15, 16), width = '6em')

```

```{r privu-percent-matrix}

rownames(table_1mode_privu$onemode_pct_df) <- colnames(table_1mode_privu$onemode_pct_df)

kable(table_1mode_privu$onemode_pct_df, caption = 'One-mode private university percent matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(1, width = '13em') %>%
  column_spec(2:15, width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
  column_spec(14:15, width = '8.5em')

```

@@

```{r privu-percent-visited-by-pubu-matrix}
rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)

kable(table_1mode_u$onemode_pct_df[c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29),c(2,3,4,5,6,8,10,11,12,14,15,19,20,26)], caption = 'For private universities, the percent of high schools visited by public universities') %>%
  kable_styling(latex_options = 'scale_down') %>%
  #column_spec(1, width = '8.5em') %>%
  column_spec(2:15, width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
  column_spec(14:15, width = '8.5em')
```

@@

<!-- FIGURES -->

```{r em-funnel, echo = FALSE, fig.align = 'center', fig.cap = "The enrollment funnel", out.width = "70%", include = FALSE, eval = FALSE}
knitr::include_graphics('./../assets/images/enrollment_funnel.png')
#![The enrollment funnel](assets/images/enrollment_funnel.png)
```

```{r nd-religion, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Order 2 ego network of University of Notre Dame, vertices colored by religion"}
include_graphics(file.path(figures_dir, 'nd_religtion.pdf'))
```

```{r events-hs-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by public research universities"}
include_graphics(file.path(figures_dir, 'events_hs_count_pubu.pdf'))
```

```{r events-hs-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by selective private universities"}
include_graphics(file.path(figures_dir, 'events_hs_count_privu.pdf'))
```

```{r actual-proportional-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, public research universities"}
include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_pubu.pdf'))
```

```{r actual-proportional-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, selective private universities"}
include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_privu.pdf'))
```

```{r plot-1mode-u, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_u.pdf')
```

```{r region-pubu-privu, echo = FALSE, fig.cap = "Geographic region of visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_region_pubu_privu.pdf'))
```

```{r religion-pubu-privu, echo = FALSE, fig.cap = "Religious affiliation of visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_religion_pubu_privu.pdf'))
```

```{r rank-pubu-privu, echo = FALSE, fig.cap = "High school ranking of visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_rank_pubu_privu.pdf'))
```

```{r race-pubu-privu, echo = FALSE, eval = FALSE, include = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privu.pdf'))
```

```{r race-pubu-privhs-pubhs, echo = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs. visited private high schools, public research universities"}
include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privhs_pubhs.pdf'))
```

```{r race-privu-privhs-pubhs, echo = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs. visited private high schools, selective private universities"}
include_graphics(file.path(figures_dir, 'ego_network_race_privu_privhs_pubhs.pdf'))
```

\newpage
\clearpage

# Supplemental Online Appendix

\pagenumbering{gobble}
\pagenumbering{arabic}
\renewcommand*{\thepage}{A\arabic{page}}
\pagestyle{fancy}
\setlength{\headheight}{15pt}

\beginsupplement

```{r pubu-count-matrix}

kable(table_1mode_pubu$onemode_df, caption = 'One-mode public university count matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(c(1), width = '13em') %>% 
  column_spec(c(14), width = '8.5em') %>% 
  column_spec(2:13, width = '7em') %>% 
  column_spec(c(7, 9, 15, 16), width = '6em')
```

```{r privu-count-matrix}

table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))

kable(table_1mode_privu$onemode_df, caption = 'One-mode private universities count matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(1, width = '8.5em') %>%
  column_spec(2:15, width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em')
```

```{r u-cluster2-percent-matrix, eval=FALSE}
kable(table_1mode_u$onemode_pct_df[cluster_2, cluster_2], caption = 'Public and private universities percent matrix (cluster 2)') %>%
  kable_styling(latex_options = 'scale_down')
```

```{r u-cluster3-percent-matrix, eval=FALSE}
kable(table_1mode_u$onemode_pct_df[cluster_3, cluster_3], caption = 'Public and private universities percent matrix (cluster 3)') %>%
  kable_styling(latex_options = 'scale_down')
```

```{r u-top-percent-matrix, eval=FALSE}
kable(table_1mode_u$onemode_pct_df[c(1,2,3,4,5,6,7,8,9),c(1,2,3,4,5,6,7,8,9)], caption = 'Public and private universities, highest degree centrality') %>%
  kable_styling(latex_options = 'scale_down')
```

```{r events-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, public research universities"}
include_graphics(file.path(figures_dir, 'events_count_pubu.pdf'))
```

```{r events-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, selective private universities"}
include_graphics(file.path(figures_dir, 'events_count_privu.pdf'))
```

>>>>

*During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[NAME THE UNIVERSITIES] We are still trying to figure out what happened.*

\bigskip

@@

Father Ryan High School is a Catholic school founded in 1925. Father Ryan is predominantly white (86%, 7% Black or Latinx) and received an "A" grade from Niche, meaning it is not ranked in the top 1,000 US private schools. In fall 2017, Father Ryan received visits from nine of the 14 private universities in our sample (including all the Catholic universities) and the same six public universities that visited Harpeth Hall, including two visits by the University of Alabama. Meanwhile, Christ Presbyterian Academy -- also not ranked in the top 1,000 private schools -- received visits from five private universities in our sample (including the three Christian universities Baylor, Texas Christian University, and Southern Methodist University). It also received visits from the University of Cincinnati, the University of South Carolina, the University of Alabama, University of Arkansas, and CU Boulder. Christ Presbyterian Academy was founded in 1985 and 94% of its students are white.

@@

@RN4758 analyzed recruiting visits to public high schools made by 15 public research universities in 2017. The authors found that 12 of the 15 universities made more visits to out-of-state schools than in-state schools. These out-of-state visits focused on affluent, predominantly white public schools. Set against the scholarship about declining state appropriations and growing nonresident enrollment [@RN3753; @RN3685], these results suggest that many public research universities prioritize enrollment from wealthy out-of-state students who can afford to pay nonresident tuition price.

Within scholarship on social mobility and social stratification, a multidisciplinary literature analyzes the relationship between private school and college [CITE]. This research observes strong links -- and student flows -- between private high schools and selective private universities [CITE]. Private schools enroll many students who can afford private university tuition. To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on links between between private school and college. We argue that these two stories have become connected because public research universities increasingly target out-of-state private schools, schools that have been the domain of selective private universities. Simply put, selective private universities and public research universities are increasingly competing for students from the same set of affluent households.

@@

<!--1. 
How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?
How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities? 
-->

1. How does the scale of visits to private high schools vary for the public research universities and selective private universities in our sample?
1. To what extent do public research universities and selective private universities visit overlapping sets of private high schools?
1. What are the characteristics of private schools that receive visits from public research universities and selective private research universities in our sample?

Both private and public universities in our sample made a disproportionate number of visits to private high schools. For public research universities, visited private schools were much more likely to be out-of-state than visited public schools. Network analyses revealed substantial overlap in the recruiting networks of universities in our sample. For several public universities (e.g., University of Alabama, University of South Carolina) their recruiting networks had more similarity to private universities (e.g., Southern Methodist University, Texas Christian University) than they did to other public universities in our sample. Results suggest that recruiting networks are substantially a function of geographic location. All universities visited a large number of private schools in their home region. However, most universities in our sample also visited a large number of private schools in the South. The private schools visited by public and private universities in our sample enrolled a much higher share of white students than the public schools visited by these universities. Surprisingly, several public universities visited sectarian private high schools at a rate similar to sectarian private universities.

This manuscript yields practical implications for public and private universities concerned about racial and socioeconomic diversity. Following the Covid-19 Pandemic, off-campus recruiting visits have bounced back because they remain the fundamental means of maintaining relationships with high school guidance counselors [CITE]. Prior research shows that that students are sensitive to recruiting interventions, including off-campus recruiting visits. Therefore, which high schools a university chooses to visit will affect the subsequent enrollment composition of the university. In the aftermath of the Supreme Court decision on race conscious admissions, public and private universities are searching for ways to increase racial diversity without running afoul of the law. The U.S. Department of Education recommends that universities expand "outreach to high schools with substantial populations of low-income students and students of color" (CITE, PX X). Most public and private universities in our sample visited a disproportionate number of private schools and these private schools tended to enroll mostly white students. We recommend that universities concerned about racial diversity should conduct an internal equity audit of their recruiting practices, for example, comparing the racial and socioeconomic characteristics of schools they visit versus schools they do not visit.

@@

An anecdote from @RN3519[p. 73] highlights the allure that prestigious private schools and affluent private school students hold for selective private colleges. Stevens accompanied an admissions officer from the College on a visit to Corbett Academy, a prestigious school for girls. The admissions officer "said with a grin, 'We're not getting Corbett's finest.'" @RN3519 (p. 73) writes that,

> Corbett consistently sent its top performers to places like Berkeley and Stanford and the top of the Ivy League \ldots [Other colleges] in the College's own peer group only had a shot at girls nearer the middle of Corbett's class. Or below the middle. Still, by most standards this excellent school's modest achievers were very good admissions prospects, which was why we were visiting. Even Corbett's less fine would enter college well prepared academically, and their generally affluent famiies could absorb the College's full tuition and board cost with little, if any, financial aid."

@@

\newpage
\clearpage
\begin{landscape}

```{r sample-characteristics}
univ_sample <- univ_sample_df %>% 
  filter(classification != 'private_libarts') %>% 
  select(classification, univ_abbrev, rank, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_p, pctfreshwh, pctfreshbl, pctfreshap, pctfreshhi, pctfreshal) %>% 
  mutate(
    classification = recode(
      classification,
      'public_research' = 'Public Research',
      'private_national' = 'Private National'
    ),
    satactcomp25 = format(round(satactcomp25), big.mark = ',', trim = T),
    satactcomp75 = format(round(satactcomp75), big.mark = ',', trim = T),
    tfuginst = str_c('\\$', format(round(tfuginst), big.mark = ',', trim = T)),
    tfugoutst = str_c('\\$', format(round(tfugoutst), big.mark = ',', trim = T)),
    ugftptfreshtot = format(round(ugftptfreshtot), big.mark = ',', trim = T),
    freshoutstpct = str_c(format(round(freshoutstpct * 100, 1), nsmall = 1), '\\%'),
    pgrnt_p = str_c(format(round(pgrnt_p, 1), nsmall = 1), '\\%'),
    pctfreshwh = str_c(format(round(pctfreshwh, 1), nsmall = 1), '\\%'),
    pctfreshbl = str_c(format(round(pctfreshbl, 1), nsmall = 1), '\\%'),
    pctfreshap = str_c(format(round(pctfreshap, 1), nsmall = 1), '\\%'),
    pctfreshhi = str_c(format(round(pctfreshhi, 1), nsmall = 1), '\\%'),
    pctfreshal = str_c(format(round(pctfreshal, 1), nsmall = 1), '\\%')
  ) %>% 
  arrange(desc(classification), rank)

names(univ_sample) <- c('Classification', 'University', 'Rank', '25th Percentile SAT/ACT Composite Score', '75th Percentile SAT/ACT Composite Score', 'In-State Tuition + Fees', 'Out-of-State Tuition + Fees', 'Total Enrolled Freshmen', 'Percent Out-of-State Freshmen', 'Percent Pell Recipients', 'Percent White Freshmen', 'Percent Black Freshmen', 'Percent Asian Freshmen', 'Percent Hispanic Freshmen', 'Percent International Freshmen')

kable(univ_sample, caption = "Characteristics of universities in analysis sample", booktabs = T, escape = F, align = 'c') %>%
  collapse_rows(columns = 1, latex_hline = 'major', valign = 'middle') %>%
  column_spec(c(2), width = '4.5cm', latex_valign = 'm') %>% 
  column_spec(c(3), width = '1.8cm', latex_valign = 'm') %>% 
  column_spec(c(4, 5), width = '3.8cm', latex_valign = 'm') %>% 
  column_spec(c(6, 8, 10:14), width = '2.4cm', latex_valign = 'm') %>% 
  column_spec(c(7), width = '2.7cm', latex_valign = 'm') %>% 
  column_spec(c(9, 15), width = '3cm', latex_valign = 'm') %>% 
  kable_styling(font_size = 13, latex_options = c('scale_down', 'hold_position'))
```

@@

```{r sample-population-characteristics}
# Source: https://docs.google.com/spreadsheets/d/1e8lnU2YhJVigEYR55tc0pijsm52WKaEua8MNaYXTtM4
# Also in methodology: https://emraresearch.org/methodology

# 49 public research
pop_pubu <- c('151351', '171100', '180461', '188030', '199193', '147703', '204857', '207388', '214777', '186380', '149222', '196088', '196097', '204796', '100751', '197036', '164155', '104179', '106397', '110635', '110644', '110653', '110662', '110671', '110680', '201885', '126614', '129020', '139959', '141574', '225511', '142285', '155317', '161253', '163286', '166629', '170976', '181464', '187985', '199120', '215293', '217484', '218663', '230764', '234076', '236948', '230728', '234030', '172644')

# 49 private national
pop_privu <- c('194824', '139658', '190150', '223232', '212054', '193900', '166027', '144050', '130794', '243744', '166683', '198419', '215062', '162928', '182670', '110404', '147767', '217156', '190415', '227757', '152080', '186131', '221999', '131496', '164988', '160755', '213543', '135726', '216597', '228246', '191241', '186867', '131159', '228875', '239105', '127060', '122436', '207971', '179159', '168148', '164924', '195030', '179867', '201645', '197708', '199847', '211440', '121150', '123961')

sample_pubu <- (univ_sample_df %>% filter(classification == 'public_research'))$univ_id
sample_privu <- (univ_sample_df %>% filter(classification == 'private_national'))$univ_id

univ_pop <- read.csv(file.path(data_dir, 'ipeds_data.csv'), header = TRUE, na.strings = c('', 'NULL', 'NA'), stringsAsFactors = FALSE, colClasses = c('unitid' = 'character')) %>% as_tibble() %>%
  filter(endyear == 2017, unitid %in% c(pop_pubu, pop_privu, sample_pubu, sample_privu)) %>% 
  select(unitid, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_n, cohortsfaef, ugftptfreshwhmf, ugftptfreshblmf, ugftptfreshapmf, ugftptfreshhimf, ugftptfreshalmf, ugftptfreshmrmf, ugftptfreshnamf, ugftptfreshunmf, ugftptfreshasmf, ugftptfreshnhmf) %>% 
  mutate(
    pgrnt_p = pgrnt_n / cohortsfaef * 100,
    pctfreshwh = ugftptfreshwhmf / ugftptfreshtot * 100,
    pctfreshbl = ugftptfreshblmf / ugftptfreshtot * 100,
    pctfreshap = ugftptfreshapmf / ugftptfreshtot * 100,  # ap = as + nh
    pctfreshhi = ugftptfreshhimf / ugftptfreshtot * 100,
    pctfreshal = ugftptfreshalmf / ugftptfreshtot * 100,
    pctfreshmr = ugftptfreshmrmf / ugftptfreshtot * 100,
    pctfreshna = ugftptfreshnamf / ugftptfreshtot * 100,
    pctfreshun = ugftptfreshunmf / ugftptfreshtot * 100,
    pctfreshas = ugftptfreshasmf / ugftptfreshtot * 100,
    pctfreshnh = ugftptfreshnhmf / ugftptfreshtot * 100
  ) %>% 
  select(unitid, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_p, pctfreshwh, pctfreshbl, pctfreshap, pctfreshhi, pctfreshal)

format_data <- function(univ_ids) {
  apply(univ_pop %>% filter(unitid %in% univ_ids) %>% select(-unitid), 2, function(x) quantile(x, probs = c(0.25, 0.5, 0.75), na.rm = T)) %>% 
    as.data.frame() %>% 
    mutate(
      satactcomp25 = format(round(satactcomp25), big.mark = ',', trim = T),
      satactcomp75 = format(round(satactcomp75), big.mark = ',', trim = T),
      tfuginst = str_c('\\$', format(round(tfuginst), big.mark = ',', trim = T)),
      tfugoutst = str_c('\\$', format(round(tfugoutst), big.mark = ',', trim = T)),
      ugftptfreshtot = format(round(ugftptfreshtot), big.mark = ',', trim = T),
      freshoutstpct = str_c(format(round(freshoutstpct * 100, 1), nsmall = 1), '\\%'),
      pgrnt_p = str_c(format(round(pgrnt_p, 1), nsmall = 1), '\\%'),
      pctfreshwh = str_c(format(round(pctfreshwh, 1), nsmall = 1), '\\%'),
      pctfreshbl = str_c(format(round(pctfreshbl, 1), nsmall = 1), '\\%'),
      pctfreshap = str_c(format(round(pctfreshap, 1), nsmall = 1), '\\%'),
      pctfreshhi = str_c(format(round(pctfreshhi, 1), nsmall = 1), '\\%'),
      pctfreshal = str_c(format(round(pctfreshal, 1), nsmall = 1), '\\%')
    ) %>% 
    t()
}

univ_pop_df <- cbind(
  format_data(sample_pubu),
  format_data(pop_pubu),
  format_data(sample_privu),
  format_data(pop_privu)
)
rownames(univ_pop_df) <- c('25th Percentile SAT/ACT Composite Score', '75th Percentile SAT/ACT Composite Score', 'In-State Tuition + Fees', 'Out-of-State Tuition + Fees', 'Total Enrolled Freshmen', 'Percent Out-of-State Freshmen', 'Percent Pell Recipients', 'Percent White Freshmen', 'Percent Black Freshmen', 'Percent Asian Freshmen', 'Percent Hispanic Freshmen', 'Percent International Freshmen')
colnames(univ_pop_df) <- rep(c('25th percentile', '50th percentile', '75th percentile'), 4)

kable(univ_pop_df, caption = "Characteristics of universities in analysis sample compared to data collection sample", booktabs = T, escape = F, align = 'c', linesep = '') %>%
  add_header_above(header = c(' ' = 1, 'Analysis sample (N=15)' = 3, 'Data collection sample (N=49)' = 3, 'Analysis sample (N=14)' = 3, 'Data collection sample (N=49)' = 3)) %>%
  add_header_above(header = c(' ' = 1, 'Public research universities' = 6, 'Selective private universities' = 6)) %>%
  kable_styling(font_size = 13, latex_options = 'scale_down') 
```

@@

```{r pubu-percent-matrix}
table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
rownames(table_1mode_pubu$onemode_pct_df) <- colnames(table_1mode_pubu$onemode_pct_df)

kable(table_1mode_pubu$onemode_pct_df, caption = 'One-mode public university percent matrix', booktabs = T, align = 'c', linesep = '') %>%
  column_spec(c(7, 9, 15), width = '5em') %>%
  column_spec(c(4, 12), width = '5.5em') %>%
  column_spec(c(6, 10, 16), width = '6em') %>%
  column_spec(c(2, 11, 13), width = '6.5em') %>%
  column_spec(c(3, 8), width = '7em') %>%
  column_spec(c(5), width = '7.5em') %>%
  column_spec(c(14), width = '8.8em') %>%
  kable_styling(font_size = 13, latex_options = 'scale_down') 
```

```{r privu-percent-matrix}
table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))
rownames(table_1mode_privu$onemode_pct_df) <- colnames(table_1mode_privu$onemode_pct_df)

kable(table_1mode_privu$onemode_pct_df, caption = 'One-mode private university percent matrix', booktabs = T, align = 'c', linesep = '') %>%
  column_spec(c(2, 3, 7:9, 11), width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
  column_spec(14:15, width = '8.5em') %>%
  kable_styling(font_size = 13, latex_options = 'scale_down') 
```

```{r privu-percent-visited-by-pubu-matrix}
table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)

kable(table_1mode_u$onemode_pct_df[c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29),c(2,3,4,5,6,8,10,11,12,14,15,19,20,26)], caption = 'For private universities, the percent of high schools visited by public universities', booktabs = T, align = 'c', linesep = '') %>%
  column_spec(c(2, 3, 7:9, 11), width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
  column_spec(14:15, width = '8.5em') %>%
  kable_styling(font_size = 13, latex_options = 'scale_down')
```

```{r pubu-percent-visited-by-privu-matrix}
table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)

kable(table_1mode_u$onemode_pct_df[c(2,3,4,5,6,8,10,11,12,14,15,19,20,26),c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29)], caption = 'For public universities, the percent of high schools visited by private universities', booktabs = T, align = 'c', linesep = '') %>%
  column_spec(c(7, 9, 15), width = '5em') %>%
  column_spec(c(4, 12), width = '5.5em') %>%
  column_spec(c(6, 10, 16), width = '6em') %>%
  column_spec(c(2, 11, 13), width = '6.5em') %>%
  column_spec(c(3, 8), width = '7em') %>%
  column_spec(c(5), width = '7.5em') %>%
  column_spec(c(14), width = '8.8em') %>%
  kable_styling(font_size = 13, latex_options = 'scale_down')
```

```{r nd-religion, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Order 2 ego network of University of Notre Dame, vertices colored by religion"}
include_graphics(file.path(figures_dir, 'nd_religion.pdf'))
```

```{r events-hs-count-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Number of visits to public and private high schools by public research universities"}
include_graphics(file.path(figures_dir, 'events_hs_count_pubu.pdf'))
```

```{r events-hs-count-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Number of visits to public and private high schools by selective private universities"}
include_graphics(file.path(figures_dir, 'events_hs_count_privu.pdf'))
```

```{r actual-proportional-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Actual versus proportional number of private school visits, public research universities"}
include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_pubu.pdf'))
```

```{r actual-proportional-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Actual versus proportional number of private school visits, selective private universities"}
include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_privu.pdf'))
```

```{r plot-1mode-u, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
knitr::include_graphics(file.path(figures_dir, 'plot_1mode_u.pdf'))
```

```{r region-pubu-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Geographic region of visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_region_pubu_privu.pdf'))
```

```{r religion-pubu-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Religious affiliation of visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_religion_pubu_privu.pdf'))
```

```{r rank-pubu-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "High school ranking of visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_rank_pubu_privu.pdf'))
```

```{r race-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs. visited private high schools, public research universities"}
include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privhs_pubhs.pdf'))
```

```{r race-privu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs. visited private high schools, selective private universities"}
include_graphics(file.path(figures_dir, 'ego_network_race_privu_privhs_pubhs.pdf'))
```

\beginsupplement
\clearpage
\newpage

```{r pubu-count-matrix}
rownames(table_1mode_pubu$onemode_df) <- colnames(table_1mode_pubu$onemode_df)

kable(table_1mode_pubu$onemode_df, caption = 'One-mode public university count matrix', booktabs = T, align = 'c', linesep = '') %>%
  column_spec(c(7, 9, 15), width = '5em') %>%
  column_spec(c(4, 12), width = '5.5em') %>%
  column_spec(c(6, 10, 16), width = '6em') %>%
  column_spec(c(2, 11, 13), width = '6.5em') %>%
  column_spec(c(3, 8), width = '7em') %>%
  column_spec(c(5), width = '7.5em') %>%
  column_spec(c(14), width = '8.8em') %>%
  kable_styling(font_size = 13, latex_options = 'scale_down') 
```

```{r privu-count-matrix}
table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))
rownames(table_1mode_privu$onemode_df) <- colnames(table_1mode_privu$onemode_df)

kable(table_1mode_privu$onemode_df, caption = 'One-mode private universities count matrix', booktabs = T, align = 'c', linesep = '') %>%
  column_spec(c(2, 3, 7:9, 11), width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
  column_spec(14:15, width = '8.5em') %>%
  kable_styling(font_size = 13, latex_options = 'scale_down') 
```

```{r events-count-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Number of visits by type and in-state vs. out-of-state, public research universities"}
include_graphics(file.path(figures_dir, 'events_count_pubu.pdf'))
```

```{r events-count-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Number of visits by type and in-state vs. out-of-state, selective private universities"}
include_graphics(file.path(figures_dir, 'events_count_privu.pdf'))
```

```{r plot-1mode-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for public institutions, colored by cluster"}
knitr::include_graphics(file.path(figures_dir, 'plot_1mode_pubu.pdf'))
```

```{r plot-1mode-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for private universities, colored by cluster"}
knitr::include_graphics(file.path(figures_dir, 'plot_1mode_privu.pdf'))
```

```{r enroll-pubu-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "12th grade enrollment of visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_enroll_pubu_privu.pdf'))
```

```{r enroll-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "12th grade enrollment of visited private high schools vs. public high schools, public research universities"}
include_graphics(file.path(figures_dir, 'ego_network_enroll_pubu_privhs_pubhs.pdf'))
```

@@
